---
title: "jstable"
output: github_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

[![Build Status](https://travis-ci.org/jinseob2kim/jstable.svg?branch=master)](https://travis-ci.org/jinseob2kim/jstable)
[![CRAN\_Status\_Badge](http://www.r-pkg.org/badges/version/jstable)](http://cran.r-project.org/package=jstable)
[![codecov](https://codecov.io/github/jinseob2kim/jstable/branch/master/graphs/badge.svg)](https://codecov.io/github/jinseob2kim/jstable)
[![GitHub issues](https://img.shields.io/github/issues/jinseob2kim/jstable.svg)](https://github.com/jinseob2kim/jstable/issues)
[![GitHub forks](https://img.shields.io/github/forks/jinseob2kim/jstable.svg)](https://github.com/jinseob2kim/jstable/network)
[![GitHub stars](https://img.shields.io/github/stars/jinseob2kim/jstable.svg)](https://github.com/jinseob2kim/jstable/stargazers)
[![GitHub license](https://img.shields.io/github/license/jinseob2kim/jstable.svg)](https://github.com/jinseob2kim/jstable/blob/master/LICENSE)
[![GitHub last commit](https://img.shields.io/github/last-commit/google/skia.svg)](https://github.com/jinseob2kim/jstable)
[![GitHub contributors](https://img.shields.io/github/contributors/jinseob2kim/jstable.svg?maxAge=2592000)](https://github.com/jinseob2kim/jstable/graphs/contributors)


Research tables from GEE, GLMM, cox mixed effect model results

## Install

```{r, eval = F}
devtools::install_github('jinseob2kim/jstable')
```

## GEE Table: from `geeglm` object from **geepack** package

```{r}
library(jstable)
library(geepack)  ## for dietox data
data(dietox)
dietox$Cu <- as.factor(dietox$Cu)
dietox$ddn = as.numeric(rnorm(nrow(dietox)) > 0)
gee01 <- geeglm (Weight ~ Time + Cu , id = Pig, data = dietox, family = gaussian, corstr = "ex")
geeglm.display(gee01)

gee02 <- geeglm (ddn ~ Time + Cu , id = Pig, data = dietox, family = binomial, corstr = "ex")
geeglm.display(gee02)
```

## Mixed model Table: `lmerMod` or `glmerMod` object from **lme4** package

```{r}
library(lme4)
l1 = lmer(Weight ~ Time + Cu + (1|Pig) + (1|Evit), data = dietox) 
lmer.display(l1, ci.ranef = T)

l2 = glmer(ddn ~ Weight + Time + (1|Pig), data= dietox, family= "binomial")
lmer.display(l2)
```


## Cox model with `frailty` or `cluster` options

```{r}
library(survival)
fit1 <- coxph(Surv(time, status) ~ ph.ecog + age + cluster(inst), lung, model = T)  ## model = T: to extract original data
fit2 <- coxph(Surv(time, status) ~ ph.ecog + age + frailty(inst), lung, model = T)
cox2.display(fit1)
cox2.display(fit2)
```

## Cox mixed effect model Table: `coxme`  object from **coxme** package

```{r}
library(coxme)
fit <- coxme(Surv(time, status) ~ ph.ecog + age + (1|inst), lung)
coxme.display(fit) 
```

## GLM for weighted data : `svyglm` object from **survey** package

```{r}
library(survey);library(jstable)
data(api)
apistrat$tt = c(rep(1, 20), rep(0, nrow(apistrat) -20))
apistrat$tt2 = factor(c(rep(0, 40), rep(1, nrow(apistrat) -40)))

dstrat<-svydesign(id=~1,strata=~stype, weights=~pw, data=apistrat, fpc=~fpc)
ds <- svyglm(api00~ell+meals+cname+mobility + tt2, design=dstrat)
ds2 <- svyglm(tt~ell+meals+cname+mobility + tt2, design=dstrat, family = quasibinomial())
svyregress.display(ds)
svyregress.display(ds2)
```

## Cox model for weighted data :`svycoxph` object from **survey** package

```{r}
data(pbc, package="survival")
pbc$sex = factor(pbc$sex)
pbc$stage = factor(pbc$stage)
pbc$randomized<-with(pbc, !is.na(trt) & trt>0)
biasmodel<-glm(randomized~age*edema,data=pbc,family=binomial)
pbc$randprob<-fitted(biasmodel)

if (is.null(pbc$albumin)) pbc$albumin<-pbc$alb ##pre2.9.0

dpbc <- svydesign(id=~1, prob=~randprob, strata=~edema, data=subset(pbc,randomized))

model <- svycoxph(Surv(time,status>0)~ sex + protime + albumin + stage,design=dpbc)
svycox.display(model)
```

